---
title: "Quarto Practice"
author: "Sofia Sarak"
format: html
editor: visual
execute: 
  warning: false
---

Suppressing warnings and messages JUST for this code chunk.

```{r}
#| warning: false #excluding all the warnings
#| message: false #excluding all messages! like the tidyverse now
#the last two lines are called "execution options", which control what is actually rendered in the quarto document
library(tidyverse)
```

Running code, but not showing code or output.

```{r}
#| include: false #R still ran this code chunk but none of it will show up in the rendered doc
#return the first 6 lines of the starwars data
head(starwars)
#return the dimensions of said data
dim(starwars)
```

Showing output, but not code.

```{r}
#| warning: false
#| echo: false #won't show code but will show output (graph)
#execution files have to be RIGHT after the {r}/the first thing in the code chunk for it to work

ggplot(data = starwars, aes(x=height, y=mass, color=mass)) + 
  geom_point() +
  labs(x = "Height (cm)", y="Mass (kg)")
```

Show only code and output.

```{r}
#| warning: false #needs to be exactly like this with the spaces.
#| fig-cap: "caption text" #adding a figure caption
#| fig-alt: "figure alt text"
ggplot(data=starwars, aes(x=height)) +
  geom_histogram(color="blue3", fill="cornflowerblue")
```

Find summary stats for Star Wars characters

```{r}
sw_height_mean1 <- mean(starwars$height) #will return NA because there are missing height values!
sw_height_mean <- mean(starwars$height, na.rm=TRUE) #will remove NA values and find the real mean!
sw_height_median <- median(starwars$height, na.rm=TRUE)
sw_height_var <- var(starwars$height, na.rm=TRUE)
sw_height_sd <- sd(starwars$height, na.rm =TRUE)
```

The mean height of the characters in Star Wars is `r round(sw_height_mean,1)` centimeters.

(when inserting code into a sentence, make sure to specify coding language -- in this case, r)
